Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-07-07 manuscript/bef_stability/manuscript.Rmd
Update biomass discussion

One has to notice that most of the empirical and experimental evidence of the
positive effect of richness on biomass production and stablity through time
comes from studies focusing on one trophic level, generally primary producers or
primary consumers. Natural ecosystems generally include
more than one or two trophic levels and it is not certain that what holds
on one trophic level hold also in multitrophic communities.
Theoretical studies showed that food web properties, such as interaction
distribution and strength, affect the distribution of biomass among adjacent
trophic levels, [@thebault_relationship_2006; @schneider_animal_2016;
@barbier_pyramids_2019]. A
large body of theoretical studies links the propagation of perturbations to the
foodweb structure [@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
or trophic chain [@shanafelt_david_w._stability_nodate; @wang_biodiversity_2016;
@barbier_pyramids_2019]. To date, we have few evidence on the relationship
between network structure and total biomass and its temporal stability in
empirical multitrophic communities.

@@

In order to describe the mechanisms driving temporal stability of biomass, we
decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
weighted average species $CV$ (\overline{CV_{sp}}) components according to
@thibaut_understanding_2013:

@@

---
# Chapeau
---

@@

Our aim was to evaluate the effects of the network structure on the total
biomass and its temporal stability in natural communities, which have been
poorly documented. To do
this we quantified interactive effects of habitat properties, species richness,
and food web structure, on the biomass and stability of fish communities, from
the ONEMA fish dataset, containing over X million individual fish samples,
across 99 locations France spanning the period 1995 to 2018.
We infered trophic
interactions networks based on body size-dependency in food diet from the
literature and prey/predator body size ratio for piscivory^[ 
We inferred trophic networks at the scale of trophic species (i.e. nodes being
body size classes) to take in account ontogenic diet shifts and that fish-fish
trophic interaction depends on body size ratio between prey and predator. On the
other side, the community metrics were defined at the species level, (i.e.
species richness, average species CV and synchrony).
].
We used SEM to
disantangle direct and indirect effects of environmental drivers, horizontal and
vertical diversity on both total biomass and biomass stability. We found that
species richness and mean trophic level had a positive effect on total
biomass. In contrast, species richness had a negative effect on temporal
stability whereas mean trophic level covaried positively.  Futhermore, we
found that the effect of species richness and mean trophic level on total
biomass and its temporal stability were not independant as species richness had
a positive effect on mean trophic level.  Finally, we found that the
magnitude of the effects of average temperature and altitude was equal or
superior to the effects of species richness and mean trophic level. Overall,
our study is unique by its level of integration, from environmental effects to
total biomass and stability, going through species richness and network
structure, and the first direct assessment of a possible joint effect of
species richness and network structure.

@@

We found that species richness increased total biomass as found in salt marshes,
grasslands and
forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
@li_relationship_2018]. The positive effect of species richness on total biomass
might be due to resource use complementarity, which is held by niche
differentiation and interspecific facilitation [@loreau_biodiversity_1998;
@loreau_partitioning_2001; @cardinale_species_2002] or might be due to positive
select effect which takes place through the dominance of the
most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
Previous research seems to indicate that resource complementarity might be the
main driver in fish communities [@carey_determining_2011].

Surprisingly found a negative relationship between temporal stability and
species richness. Overall, it contrasts with experimental studies in
grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
and even in natural communities [@olivier_independent_nodate] where positive
relationships are typically found between temporal stability and species
richness. In streams as well, @franssen_annual_2011 found that species richness
increased temporal stability. However other studies found a opposite relationship
in natural grassland [@yang_effects_2011] or a marginal one
[@declerck_species_2006] in natural forests. Further investigations are needed
to identify the mechanisms behind those contrasting patterns. A first step is to
look at the effects of species richness on synchrony and $\overline{CV_{sp}}$,
which constitute the two components of temporal stability quantified as CV
[@loreau_species_2008; @thibaut_understanding_2013].

The negative effect of species richness on synchrony, thereby increasing
stability, was expected. Whereas the positive effect of species richness on
$\overline{CV_{sp}}$, thereby decreasing stability, was more intriguing. Species
richness can reduce synchrony through decrease of population size, thus
raising the role of demographic stochasticity [@loreau_species_2008] but also in
the case where species have different responses to environmental variation
[@loreau_species_2008]. Two empirical studies found ... that mechanisms behind
synchrony was ...

However a negative effect of species richness on
both population ($\overline{CV_{sp}}$) and community stability can arise the
biomass distribution across population is strongly uneven and that the biomass
variance of population increases much faster than its mean
[@thibaut_understanding_2013].

@@

- But @thebault_relationship_2006 with the same mecanisms on vertical and
  horizontal diversity

@@

mean trophic level had a positive effect on biomass stability by its negative
effect on CVsp (i.e. positive effect on average species stability). It means
that species at higher trophic level are more stable than the species at lower
trophic levels. @shanafelt_david_w._stability_nodate and @barbier_pyramids_2019
found the same pattern with pure trophic chain models. They have shown that
strong top-down control can generate this pattern but it is not
clear if this theoretical prediction holds when considering omnivorous species
(i.e not a pure food chain) [@wang_biodiversity_2016] and if other mechanisms
can generate the same pattern [@thibaut_understanding_2013].
Another explanation is that the fishes at higher trophic levels are not more
stable themselves, but rather allow for stronger top-down control and resource
complementarity and thus reduce biomass fluctuations [@rooney_structural_2006;
@neutel_reconciling_2007]. However, the ontogenic nature of the trophic
networks complicate the interpretation from the network to population
perspective. Over its life span, a given fish will change of diet and thus move
upward in the trophic chain. The dynamic of a given species composed
of several trophic species can thus be a mix of the dynamics of several trophic
levels, plus the oscillatory dynamics of the cohorts [@townsend_population_1989;
@medvinsky_modelling_2015]. Then, there is a clear need for a better
understanding of how the dynamics of pure food chain models would be affected by
inclusion of omnivory and ontogeny.

@@

>>>>

One has to notice that most of the empirical and experimental evidence of the
positive effect of richness on biomass production and stablity through time
comes from studies focusing on one trophic level, generally primary producers or
primary consumers. Natural ecosystems generally include
more than one or two trophic levels and it is not certain that what holds
on one trophic level hold also in multitrophic communities.
Theoretical studies showed that food web properties, such as interaction
distribution and strength, affect the distribution of biomass among adjacent
trophic levels, [@thebault_relationship_2006; @schneider_animal_2016;
@barbier_pyramids_2019]. A
large body of theoretical studies links the propagation of perturbations to the
foodweb structure [@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
or trophic chain [@shanafelt_stability_nodate; @wang_biodiversity_2016;
@barbier_pyramids_2019]. To date, we have few evidence on the relationship
between network structure and total biomass and its temporal stability in
empirical multitrophic communities.

@@

In order to describe the mechanisms driving temporal stability of biomass, we
decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
@thibaut_understanding_2013:

@@

@@

Our aim was to evaluate the effects of the network structure on the total
biomass and its temporal stability in natural communities, which have been
poorly documented. To do so, we quantified the effects, directs and indirects,
of habitat properties, species richness, and food web structure, on the biomass
and stability of fish communities, from the ONEMA fish dataset, containing over
X million individual fish samples, across 99 locations France spanning the
period 1995 to 2018.  We infered trophic interactions networks based on body
size-dependency in food diet from the literature and prey/predator body size
ratio for piscivory^[ We inferred trophic networks at the scale of trophic
species (i.e. nodes being body size classes) to take in account ontogenic diet
shifts and that fish-fish trophic interaction depends on body size ratio between
prey and predator. On the other side, the community metrics were defined at the
species level, (i.e.  species richness, average species CV and synchrony).  ].
We built structural equation models to disantangle the direct and indirect
effects of environmental drivers, species richness and network structure on both
total biomass and biomass stability.  We found that species richness and mean
trophic level had a positive effect on total biomass. In contrast, species
richness had a negative effect on temporal stability whereas mean trophic level
covaried positively.  Futhermore, we found that the effect of species richness
and mean trophic level on total biomass and its temporal stability were not
independant as species richness had a positive effect on mean trophic level.
Finally, we found that the magnitude of the effects of average temperature and
altitude was equal or superior to the effects of species richness and mean
trophic level. Overall, our study is unique by its level of integration, from
environmental effects to total biomass and stability, going through species
richness and network structure, and the first direct assessment of a possible
joint effect of species richness and network structure.

@@

We found that species richness increased total biomass as found in salt marshes,
grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018]. The positive effect of species
richness on total biomass might be due to resource use complementarity, which is
held by niche differentiation and interspecific facilitation
[@loreau_biodiversity_1998; @loreau_partitioning_2001; @cardinale_species_2002]
or might be due to positive select effect which takes place through the
dominance of the most productive species [@tilman_plant_1997;
@loreau_partitioning_2001]. Previous research seems to indicate that resource
complementarity might be the main driver in fish communities
[@carey_determining_2011] but futher invesgations are needed to assess the
dominance of this mecanism in aquatic communities and more generally in food
webs.

Surprisingly found a negative relationship between temporal stability and
species richness. Overall, it contrasts with experimental studies in
grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
and even in natural communities [@olivier_independent_nodate] where positive
relationships are typically found between temporal stability and species
richness. In streams as well, @franssen_annual_2011 found that species richness
increased temporal stability. However other studies found a opposite relationship
in natural grassland [@yang_effects_2011] or a marginal one
[@declerck_species_2006] in natural forests. Further investigations are needed
to identify the mechanisms behind those contrasting patterns. A first step is 
be to look at the effects of species richness on synchrony and
$\overline{CV_{sp}}$, which constitute the two components of temporal stability
quantified as CV [@loreau_species_2008; @thibaut_understanding_2013].

We found that species richness decreases synchrony, thereby increasing
stability. Species richness can reduce synchrony through decrease of population
size, thus raising the role of demographic stochasticity [@loreau_species_2008]
but also in the case where species have different responses to environmental
variation [@loreau_species_2008]. While
a negative effect of species richness on synchrony is generally found in
experimental grasslands [@isbell_biodiversity_2009; @roscher_identifying_2011],
no relation has been found in natural forests [@declerck_species_2006], but
negative relationships have been found in natural communities of birds, bats,
grasslands, bats and butterflies [@bluthgen_land_2016;
@olivier_independent_nodate]. Our study thus highlights that species richness
might also decrease synchrony in empirical trophic communities.

Whereas the positive effect of species richness on $\overline{CV_{sp}}$, thereby
decreasing stability, was more intriguing. Indeed, precedent studies found that
constrasting results. For example, @olivier_independent_nodate reported negative, neutral and
positive effect of species richness on $\overline{CV_{sp}}$ in respectively
butterfly, bat and birds communities. @thibaut_understanding_2013 proposed that
two ingredients can generate a positive effect of species richness on
population ($\overline{CV_{sp}}$) stability: a strongly uneven biomass
distribution across populationand that the biomass variance
of population increases much faster than its mean.

@@

@@

mean trophic level had a positive effect on biomass stability by its negative
effect on CVsp (i.e. positive effect on average species stability). It means
that species at higher trophic level are more stable than the species at lower
trophic levels. @shanafelt_stability_nodate and @barbier_pyramids_2019
found the same pattern with pure trophic chain models. They have shown that
strong top-down control can generate this pattern but it is not
clear if this theoretical prediction holds when considering omnivorous species
(i.e not a pure food chain) [@wang_biodiversity_2016] and if other mechanisms
can generate the same pattern [@thibaut_understanding_2013].
Another explanation is that the fishes at higher trophic levels are not more
stable themselves, but rather allow for stronger top-down control and resource
complementarity and thus reduce biomass fluctuations [@rooney_structural_2006;
@neutel_reconciling_2007]. However, the ontogenic nature of the trophic
networks complicate the interpretation from the network to population
perspective. Over its life span, a given fish will change of diet and thus move
upward in the trophic chain. The dynamic of a given species composed
of several trophic species can thus be a mix of the dynamics of several trophic
levels, plus the oscillatory dynamics of the cohorts [@townsend_population_1989;
@medvinsky_modelling_2015]. Then, there is a clear need for a better
understanding of how the dynamics of pure food chain models would be affected by
inclusion of omnivory and ontogeny.

@@

In
trophic communities,  additionnaly to the **portefolio effect**, the importance
of trophic interactions on synchrony (mal dit).
